First steps in synthetic algebraic geometry

### 2017-03-16 snippets/qcoh.tex
Easy scholium of the proof

\newtheorem{prop}[defn]{Proposition}
\newtheorem{cor}[defn]{Corollary}
\newtheorem{lemma}[defn]{Lemma}
\newtheorem{thm}[defn]{Theorem}

@@

In situation~(2), we employ the technique of approximating general~$S$-schemes
by~$S$-schemes of finite presentation. Specifically, let~$f : T \to S$ be an
arbitrary~$S$-scheme contained in the site used to define~$\Zar(S)$. Without
loss of generality, we may assume that~$T$ is an affine scheme. Thus~$T$ is
quasicompact and quasiseparated, and~$S$ is quasiseparated. We may therefore
apply the lemma of relative approximation~\stacksproject{09MV} to deduce
that~$T$ is a directed limit of an inverse system of~$S$-schemes~$f_i : T_i \to
S$ of finite presentation with affine transition maps. These~$S$-schemes
inherit quasicompactness and quasiseparatedness from~$S$. Therefore we can
apply a comparison result on the categories of quasicoherent
modules~\stacksproject{01Z0}:
\[
  E(T) = E(\lim_i T_i) \cong \colim_i E(T_i) \cong
  \colim_i \Gamma(T_i, f_i^* \E_0)
  \cong \Gamma(T, f^* \E_0). \qedhere
\]
\end{proof}

>>>>

\newtheorem{prop}[defn]{Proposition}
\newtheorem{cor}[defn]{Corollary}
\newtheorem{lemma}[defn]{Lemma}
\newtheorem{thm}[defn]{Theorem}
\newtheorem{scholium}[defn]{Scholium}

@@

In situation~(2), we employ the technique of approximating general~$S$-schemes
by~$S$-schemes of finite presentation. Specifically, let~$f : T \to S$ be an
arbitrary~$S$-scheme contained in the site used to define~$\Zar(S)$. Without
loss of generality, we may assume that~$T$ is an affine scheme. Thus~$T$ is
quasicompact and quasiseparated, and~$S$ is quasiseparated by assumption. We may therefore
apply the lemma of relative approximation~\stacksproject{09MV} to deduce
that~$T$ is a directed limit of an inverse system of~$S$-schemes~$f_i : T_i \to
S$ of finite presentation with affine transition maps. These~$S$-schemes
are contained in the site used to define~$\Zar(S)$. Furthermore, they inherit
quasicompactness and quasiseparatedness from~$S$. Therefore we can apply a
comparison result on the categories of quasicoherent
modules~\stacksproject{01Z0}:
\[
  E(T) = E(\lim_i T_i) \cong \colim_i E(T_i) \cong
  \colim_i \Gamma(T_i, f_i^* \E_0)
  \cong \Gamma(T, f^* \E_0). \qedhere
\]
\end{proof}

\begin{scholium}Let~$E \in \Zar(S)$ be a quasicoherent~$\affl$-module.
Let~$A \in \Zar(S)$ be a quasicoherent~$\affl$-algebra such that~$\Spec(A) \in
\Zar(S)$ is representable by an object of the site used to define~$\Zar(S)$.
Then the canonical morphism
\[ E \otimes_\affl A \longrightarrow [\Spec(A), E] \]
is an isomorphism.
\end{scholium}

\begin{proof}The second paragraph of the proof of
Theorem~\ref{thm:qcoh-big-char} applies.\end{proof}

% PSh
